---
title: "CatchComparison"
author: "phoebe.woodworth-jefcoats@noaa.gov"
---

# Purpose
The purpose of this script is to compare the observed and modeled catch spectra.
It started out just looking at a single model run, and then grew to include a 
bunch of runs for comparison.

# Prep
Prepare the environment by loading packages and data.  
```{r}
library(mizer) # the model
library(tidyverse, quietly = TRUE) # for working with data 
library(here) # file path management that's agnostic about your operating system
```

```{r}
pelagic_species_params <- read_csv(here("Pelagic_params.csv"), show_col_types = FALSE)
pelagic_interaction <- read.csv(here("Pelagic_interaction.csv"), row.names = 1)
pelagic_gear_params <- read.csv(here("Pelagic_gear_params_25_1.csv"), row.names = 1)

ObsDeep <- read_csv(here("ModelBuild", "FisheryData", "DeepSet_CatchAtSize.csv"), show_col_types = FALSE)
ObsShal <- read_csv(here("ModelBuild", "FisheryData", "ShallowSet_CatchAtSize.csv"), show_col_types = FALSE)

ModDeep_25_1 <- read_csv(here("ModelBuild", "FisheryData", "DeepSet_CatchAtSize_steady_25_1.csv"), show_col_types = FALSE)
ModDeep_25_5 <- read_csv(here("ModelBuild", "FisheryData", "DeepSet_CatchAtSize_steady_25_5.csv"), show_col_types = FALSE)
ModDeep_35_1 <- read_csv(here("ModelBuild", "FisheryData", "DeepSet_CatchAtSize_steady_35_1.csv"), show_col_types = FALSE)
ModDeep_35_5 <- read_csv(here("ModelBuild", "FisheryData", "DeepSet_CatchAtSize_steady_35_5.csv"), show_col_types = FALSE)
ModDeep_50_1 <- read_csv(here("ModelBuild", "FisheryData", "DeepSet_CatchAtSize_steady_50_1.csv"), show_col_types = FALSE)
ModDeep_50_5 <- read_csv(here("ModelBuild", "FisheryData", "DeepSet_CatchAtSize_steady_50_5.csv"), show_col_types = FALSE)
ModShal_25_1 <- read_csv(here("ModelBuild", "FisheryData", "ShallowSet_CatchAtSize_steady_25_1.csv"), show_col_types = FALSE)
ModShal_25_5 <- read_csv(here("ModelBuild", "FisheryData", "ShallowSet_CatchAtSize_steady_25_5.csv"), show_col_types = FALSE)
ModShal_35_1 <- read_csv(here("ModelBuild", "FisheryData", "ShallowSet_CatchAtSize_steady_35_1.csv"), show_col_types = FALSE)
ModShal_35_5 <- read_csv(here("ModelBuild", "FisheryData", "ShallowSet_CatchAtSize_steady_35_5.csv"), show_col_types = FALSE)
ModShal_50_1 <- read_csv(here("ModelBuild", "FisheryData", "ShallowSet_CatchAtSize_steady_50_1.csv"), show_col_types = FALSE)
ModShal_50_5 <- read_csv(here("ModelBuild", "FisheryData", "ShallowSet_CatchAtSize_steady_50_5.csv"), show_col_types = FALSE)
```

We added `catchability` to the species params because it made it easier to track
the references we used and allowed us to easily add them to the gear params. We're
going to remove that column now, just to avoid any possible confusion down the
line.
```{r}
pelagic_species_params <- pelagic_species_params |>
  mutate(catchability = NULL)
```

We're going to set up the mizer parameters so that it's easier to plot things.
```{r}
# Set effort
effort <- c(DeepSet = 0.985, ShallowSet = 0.015)
pelagic_params <- newMultispeciesParams(species_params = pelagic_species_params,
                                        gear_params = pelagic_gear_params,
                                        interaction = pelagic_interaction,
                                        initial_effort = effort,
                                        n = 0.75, p = 0.75,
                                        w_pp_cutoff = 455400)
```

Simplify some things:
```{r}
# Access the consumer size classes (w) and bin widths (dw) 
w <- pelagic_params@w
dw <- pelagic_params@dw

# Isolate the species names, too, to make things easier later on
sp <- pelagic_params@species_params$species
```


Remember, for the deep set, only ~20% of sets are observed and only every third
fish is measured.  So we need to multiply abundance by 0.066.
For the shallow set, every set is observerd and only every third fish is measured.
So we need to multiply abundance by 0.33.

Look at the correlations.
```{r}
r_Vals_25_1 <- matrix(numeric(), nrow = 18, ncol = 2)
r_Vals_25_5 <- matrix(numeric(), nrow = 18, ncol = 2)
r_Vals_35_1 <- matrix(numeric(), nrow = 18, ncol = 2)
r_Vals_35_5 <- matrix(numeric(), nrow = 18, ncol = 2)
r_Vals_50_1 <- matrix(numeric(), nrow = 18, ncol = 2)
r_Vals_50_5 <- matrix(numeric(), nrow = 18, ncol = 2)
p_Vals_25_1 <- matrix(numeric(), nrow = 18, ncol = 2)
p_Vals_25_5 <- matrix(numeric(), nrow = 18, ncol = 2)
p_Vals_35_1 <- matrix(numeric(), nrow = 18, ncol = 2)
p_Vals_35_5 <- matrix(numeric(), nrow = 18, ncol = 2)
p_Vals_50_1 <- matrix(numeric(), nrow = 18, ncol = 2)
p_Vals_50_5 <- matrix(numeric(), nrow = 18, ncol = 2)
rownames(r_Vals_25_1) <- sp
rownames(r_Vals_25_5) <- sp
rownames(r_Vals_35_1) <- sp
rownames(r_Vals_35_5) <- sp
rownames(r_Vals_50_1) <- sp
rownames(r_Vals_50_5) <- sp
rownames(p_Vals_25_1) <- sp
rownames(p_Vals_25_5) <- sp
rownames(p_Vals_35_1) <- sp
rownames(p_Vals_35_5) <- sp
rownames(p_Vals_50_1) <- sp
rownames(p_Vals_50_5) <- sp
colnames(r_Vals_25_1) <- c("Deep", "Shallow")
colnames(r_Vals_25_5) <- c("Deep", "Shallow")
colnames(r_Vals_35_1) <- c("Deep", "Shallow")
colnames(r_Vals_35_5) <- c("Deep", "Shallow")
colnames(r_Vals_50_1) <- c("Deep", "Shallow")
colnames(r_Vals_50_5) <- c("Deep", "Shallow")
colnames(p_Vals_25_1) <- c("Deep", "Shallow")
colnames(p_Vals_25_5) <- c("Deep", "Shallow")
colnames(p_Vals_35_1) <- c("Deep", "Shallow")
colnames(p_Vals_35_5) <- c("Deep", "Shallow")
colnames(p_Vals_50_1) <- c("Deep", "Shallow")
colnames(p_Vals_50_5) <- c("Deep", "Shallow")

for (s in seq(1, 18, 1)){
  deep_hold_25_1 <- cor.test(as.numeric(ObsDeep[s,]), (as.numeric(ModDeep_25_1[s,])*0.066))
  deep_hold_25_5 <- cor.test(as.numeric(ObsDeep[s,]), (as.numeric(ModDeep_25_5[s,])*0.066))
  deep_hold_35_1 <- cor.test(as.numeric(ObsDeep[s,]), (as.numeric(ModDeep_35_1[s,])*0.066))
  deep_hold_35_5 <- cor.test(as.numeric(ObsDeep[s,]), (as.numeric(ModDeep_35_5[s,])*0.066))
  deep_hold_50_1 <- cor.test(as.numeric(ObsDeep[s,]), (as.numeric(ModDeep_50_1[s,])*0.066))
  deep_hold_50_5 <- cor.test(as.numeric(ObsDeep[s,]), (as.numeric(ModDeep_50_5[s,])*0.066))
  shal_hold_25_1 <- cor.test(as.numeric(ObsShal[s,]), (as.numeric(ModShal_25_1[s,])*0.33))
  shal_hold_25_5 <- cor.test(as.numeric(ObsShal[s,]), (as.numeric(ModShal_25_5[s,])*0.33))
  shal_hold_35_1 <- cor.test(as.numeric(ObsShal[s,]), (as.numeric(ModShal_35_1[s,])*0.33))
  shal_hold_35_5 <- cor.test(as.numeric(ObsShal[s,]), (as.numeric(ModShal_35_5[s,])*0.33))
  shal_hold_50_1 <- cor.test(as.numeric(ObsShal[s,]), (as.numeric(ModShal_50_1[s,])*0.33))
  shal_hold_50_5 <- cor.test(as.numeric(ObsShal[s,]), (as.numeric(ModShal_50_5[s,])*0.33))
  
  if (deep_hold_25_1$p.value < 0.05) {
    r_Vals_25_1[s,1] <- deep_hold_25_1$estimate
    p_Vals_25_1[s,1] <- deep_hold_25_1$p.value
  }
  if (deep_hold_25_5$p.value < 0.05) {
    r_Vals_25_5[s,1] <- deep_hold_25_5$estimate
    p_Vals_25_5[s,1] <- deep_hold_25_5$p.value
  }
  if (deep_hold_35_1$p.value < 0.05) {
    r_Vals_35_1[s,1] <- deep_hold_35_1$estimate
    p_Vals_35_1[s,1] <- deep_hold_35_1$p.value
  }
  if (deep_hold_35_5$p.value < 0.05) {
    r_Vals_35_5[s,1] <- deep_hold_35_5$estimate
    p_Vals_35_5[s,1] <- deep_hold_35_5$p.value
  }
  if (deep_hold_50_1$p.value < 0.05) {
    r_Vals_50_1[s,1] <- deep_hold_50_1$estimate
    p_Vals_50_1[s,1] <- deep_hold_50_1$p.value
  }
  if (deep_hold_50_5$p.value < 0.05) {
    r_Vals_50_5[s,1] <- deep_hold_50_5$estimate
    p_Vals_50_5[s,1] <- deep_hold_50_5$p.value
  }
  
  if (shal_hold_25_1$p.value < 0.05) {
    r_Vals_25_1[s,2] <- shal_hold_25_1$estimate
    p_Vals_25_1[s,2] <- shal_hold_25_1$p.value
  }
  if (shal_hold_25_5$p.value < 0.05) {
    r_Vals_25_5[s,2] <- shal_hold_25_5$estimate
    p_Vals_25_5[s,2] <- shal_hold_25_5$p.value
  }
  if (shal_hold_35_1$p.value < 0.05) {
    r_Vals_35_1[s,2] <- shal_hold_35_1$estimate
    p_Vals_35_1[s,2] <- shal_hold_35_1$p.value
  }
  if (shal_hold_35_5$p.value < 0.05) {
    r_Vals_35_5[s,2] <- shal_hold_35_5$estimate
    p_Vals_35_5[s,2] <- shal_hold_35_5$p.value
  }
  if (shal_hold_50_1$p.value < 0.05) {
    r_Vals_50_1[s,2] <- shal_hold_50_1$estimate
    p_Vals_50_1[s,2] <- shal_hold_50_1$p.value
  }
  if (shal_hold_50_5$p.value < 0.05) {
    r_Vals_50_5[s,2] <- shal_hold_50_5$estimate
    p_Vals_50_5[s,2] <- shal_hold_50_5$p.value
  }
}

# write_csv(as.data.frame(r_Vals_25_1), here("ModelBuild", "FisheryData", "CatchComparison_r_steady_25_1.csv"))
# write_csv(as.data.frame(r_Vals_25_5), here("ModelBuild", "FisheryData", "CatchComparison_r_steady_25_5.csv"))
# write_csv(as.data.frame(r_Vals_35_1), here("ModelBuild", "FisheryData", "CatchComparison_r_steady_35_1.csv"))
# write_csv(as.data.frame(r_Vals_35_5), here("ModelBuild", "FisheryData", "CatchComparison_r_steady_35_5.csv"))
# write_csv(as.data.frame(r_Vals_50_1), here("ModelBuild", "FisheryData", "CatchComparison_r_steady_50_1.csv"))
# write_csv(as.data.frame(r_Vals_50_5), here("ModelBuild", "FisheryData", "CatchComparison_r_steady_50_5.csv"))
# 
# write_csv(as.data.frame(p_Vals_25_1), here("ModelBuild", "FisheryData", "CatchComparison_p_steady_25_1.csv"))
# write_csv(as.data.frame(p_Vals_25_5), here("ModelBuild", "FisheryData", "CatchComparison_p_steady_25_5.csv"))
# write_csv(as.data.frame(p_Vals_35_1), here("ModelBuild", "FisheryData", "CatchComparison_p_steady_35_1.csv"))
# write_csv(as.data.frame(p_Vals_35_5), here("ModelBuild", "FisheryData", "CatchComparison_p_steady_35_5.csv"))
# write_csv(as.data.frame(p_Vals_50_1), here("ModelBuild", "FisheryData", "CatchComparison_p_steady_50_1.csv"))
# write_csv(as.data.frame(p_Vals_50_5), here("ModelBuild", "FisheryData", "CatchComparison_p_steady_50_5.csv"))

```


Plot things
```{r}
# pdf(here("ModelBuild", "FisheryData", "DeepSet_InitialCatchComparisons.pdf"), width = 10, height = 8)
par(mfrow = c(3,6))
par(pin = c(1,1))
for (s in seq(1, 18, 1)) {
  plot(log10(w), log10(ObsDeep[s,]), type = "l", xlim = c(-3, 6), ylim = c(0, 5),
       main = sp[s], col = "black",
       xlab = "log10(body weight in grams)", ylab = "log10(number caught)")
  lines(x = log10(w), y = log10(ModDeep_25_1[s,]*0.066), col = "darkorchid", xlim = c(-3,6), ylim = c(0,5))
  lines(x = log10(w), y = log10(ModDeep_25_5[s,]*0.066), col = "darkorchid1", xlim = c(-3,6), ylim = c(0,5))
  lines(x = log10(w), y = log10(ModDeep_35_1[s,]*0.066), col = "seagreen", xlim = c(-3,6), ylim = c(0,5))
  lines(x = log10(w), y = log10(ModDeep_35_5[s,]*0.066), col = "seagreen3", xlim = c(-3,6), ylim = c(0,5))
  lines(x = log10(w), y = log10(ModDeep_50_1[s,]*0.066), col = "steelblue", xlim = c(-3,6), ylim = c(0,5))
  lines(x = log10(w), y = log10(ModDeep_50_5[s,]*0.066), col = "steelblue1", xlim = c(-3,6), ylim = c(0,5))
  text(x = -2, y = 4.5, signif(r_Vals_25_1[s,1], 2), col = "darkorchid", xlim = c(-3,6), ylim = c(0,5))
  text(x = -2, y = 4.0, signif(r_Vals_25_5[s,1], 2), col = "darkorchid1", xlim = c(-3,6), ylim = c(0,5))
  text(x = -2, y = 3.5, signif(r_Vals_35_1[s,1], 2), col = "seagreen", xlim = c(-3,6), ylim = c(0,5))
  text(x = -2, y = 3.0, signif(r_Vals_35_5[s,1], 2), col = "seagreen3", xlim = c(-3,6), ylim = c(0,5))
  text(x = -2, y = 2.5, signif(r_Vals_50_1[s,1], 2), col = "steelblue", xlim = c(-3,6), ylim = c(0,5))
  text(x = -2, y = 2.0, signif(r_Vals_50_5[s,1], 2), col = "steelblue1", xlim = c(-3,6), ylim = c(0,5))
  if (s == 3 | s == 13 | s == 16) {
    points(log10(w), log10(ObsDeep[s,]), xlim = c(-3, 6), ylim = c(0, 5), col = "black")
  }
}
# dev.off()

# pdf(here("ModelBuild", "FisheryData", "ShallowSet_InitialCatchComparisons.pdf"), width = 10, height = 8)
par(mfrow = c(3,6))
par(pin = c(1,1))
for (s in seq(1, 18, 1)) {
  plot(log10(w), log10(ObsShal[s,]), type = "l", xlim = c(-3, 6), ylim = c(0, 4),
       main = sp[s], col = "black",
       xlab = "log10(body weight in grams)", ylab = "log10(number caught)")
  lines(x = log10(w), y = log10(ModShal_25_1[s,]*0.33), col = "darkorchid", xlim = c(-3,6), ylim = c(0,4))
  lines(x = log10(w), y = log10(ModShal_25_5[s,]*0.33), col = "darkorchid1", xlim = c(-3,6), ylim = c(0,4))
  lines(x = log10(w), y = log10(ModShal_35_1[s,]*0.33), col = "seagreen", xlim = c(-3,6), ylim = c(0,4))
  lines(x = log10(w), y = log10(ModShal_35_5[s,]*0.33), col = "seagreen3", xlim = c(-3,6), ylim = c(0,4))
  lines(x = log10(w), y = log10(ModShal_50_1[s,]*0.33), col = "steelblue", xlim = c(-3,6), ylim = c(0,4))
  lines(x = log10(w), y = log10(ModShal_50_5[s,]*0.33), col = "steelblue1", xlim = c(-3,6), ylim = c(0,4))
  text(x = -2, y = 3.5, signif(r_Vals_25_1[s,2], 2), col = "darkorchid", xlim = c(-3,6), ylim = c(0,4))
  text(x = -2, y = 3.0, signif(r_Vals_25_5[s,2], 2), col = "darkorchid1", xlim = c(-3,6), ylim = c(0,4))
  text(x = -2, y = 2.5, signif(r_Vals_35_1[s,2], 2), col = "seagreen", xlim = c(-3,6), ylim = c(0,4))
  text(x = -2, y = 2.0, signif(r_Vals_35_5[s,2], 2), col = "seagreen3", xlim = c(-3,6), ylim = c(0,4))
  text(x = -2, y = 1.5, signif(r_Vals_50_1[s,2], 2), col = "steelblue", xlim = c(-3,6), ylim = c(0,4))
  text(x = -2, y = 1.0, signif(r_Vals_50_5[s,2], 2), col = "steelblue1", xlim = c(-3,6), ylim = c(0,4))
  if (s == 3 | s == 13 | s == 16) {
    points(log10(w), log10(ObsShal[s,]), xlim = c(-3, 6), ylim = c(0,4), col = "black")
  }
}
# dev.off()
```


