---
title: "CatchSpectra"
output: html_document
---

# Purpose
The purpose of this script is to separate observed trips into deep- and 
shallow-set trips and create size spectra for the 18 species in our mizer model.

There are a few steps to this.  On the mizer side, we need to load our fledgling 
model parameters into mizer to get the consumer size classes.  These are the 
classes we're going to bin the observed catch into.  On the observer data side,
we need to separate out the trips and then the species (or you could do species
and then trips—either way works).  Then, we'll bin them and create size spectra.

# Set up the environment
Let's load some packages that we're going to need for what we're doing.
```{r}
library(tidyverse, quietly = TRUE) # handy for working with data
library(here) # OS agnostic file management
library(mizer) # For creating the size classes we need
```

# Mizer info
We're going to load our parameters, create a multispecies mizer model with them,
and then keep just the bin sizes and bin widths, species names, and species 
parameters (because we need the *a* and *b* values for L-W conversions).  
 
For more on `w` and `dw`, see <https://sizespectrum.org/mizer/articles/model_description.html>,
specifically Size Spectrum Dynamics > Consumer densities > Details.

```{r}
# Load species parameters and interaction matrix
pelagic_species_params <- read_csv(here("Pelagic_params.csv"), show_col_types = FALSE)
pelagic_interaction <- read.csv(here("Pelagic_interaction.csv"), row.names = 1)

# Create multispecies model
pelagic_params <- newMultispeciesParams(species_params = pelagic_species_params,
                                       interaction = pelagic_interaction,
                                       initial_effort = 0,
                                       n = 0.75, p = 0.75)

# Access the consumer size classes (w) and bin widths (dw) 
w <- pelagic_params@w
dw <- pelagic_params@dw

# We're going to turn these into data frames so that we can write them as csvs for 
# future use.  
write_csv(data.frame(w), "mizer_w.csv", col_names = FALSE)
write_csv(data.frame(dw), "mizer_dw.csv", col_names = FALSE)

# Isolate the species names, too, to make things easier later on
sp <- pelagic_params@species_params$species

# Clean up
rm(list = setdiff(ls(), c("w", "dw", "sp", "pelagic_species_params")))
```
 
# Observer info
Now we can load the observer info and work with it.  
```{r}
ObsCatch <- readRDS("ObsCatch_Details_HIonly.rds")
```

Beginning with trip 2060, observers have measured every third fish.  Step one is
to filter to those trips and clean up.
```{r}
# Strip off the "LL" that starts all the trip numbers and turn the remainder into
# numbers
ObsCatch$TRIP_NUM <- as.numeric(str_sub(ObsCatch$TRIP_NUM, 3, 6))

# Filter to trip 2060+
ObsCatch <- ObsCatch |>
  filter(TRIP_NUM >= 2060)

# Filter out 2025 (likely a partial year given the time of download)
ObsCatch <- ObsCatch |>
  filter(year(HAUL_BEGIN_DATETIME) < 2025)

# We can also remove the EXPR_TRIP_TYPE_ID column because we already filtered it
# to be NA-only in ObserverCombine.Rmd
ObsCatch <- ObsCatch |>
  mutate(EXPR_TRIP_TYPE_ID = NULL)

# And we want to turn the species codes into numbers
ObsCatch <- ObsCatch |>
  mutate_at(c('SPECIES_CODE'), as.numeric)
```

Separate deep and shallow sets.  Clean up.
```{r}
ObsDeep <- ObsCatch |>
  filter(HKS_PER_FLT >= 15)

ObsShal <- ObsCatch |>
  filter(HKS_PER_FLT < 15)

# Note that all rows are accounted for:
# dim(ObsCatch)[1] - (dim(ObsDeep)[1] + dim(ObsShal)[1]) is equal in size to
# test <- which(is.na(ObsCatch$HKS_PER_FLT))

rm(ObsCatch)
```

Now we need to separate by species.  This part is tedious.  If there's a better 
way to do it, I would love the tip.  Please create an issue or a pull request.
Our end goal is two 18x100 data frames that have a row for each species and a 
column for each size bin.  The values are the approximate counts at size.  There
are a bunch of intermediate steps to get here, which is the tedious part.  But, 
the end result should be pretty useful and save us time down the road.
```{r}
# Build empty matrices
DeepN <- matrix(NA, 
                nrow = length(sp), ncol = length(w),
                dimnames = list(species = sp, w = w))
ShalN <- matrix(NA, 
                nrow = length(sp), ncol = length(w),
                dimnames = list(species = sp, w = w))

# And keep track of how many measurements there are for each fish
DeepN_n <- matrix(NA, 
                  nrow = length(sp), ncol = 1,
                  dimnames = list(species = sp, n = "count"))
ShalN_n <- matrix(NA, 
                  nrow = length(sp), ncol = 1,
                  dimnames = list(species = sp, n = "count"))

# Loop through each species/row
# Filter deep and shallow to said species
# Convert length to weight
# Loop through each size bin, summing obs in that size
# Note: we'd need to divide counts by dw to match mizer N or
# multiply mizer N by dw to get this (we're going to do the latter)
for (r in seq(1, length(sp), 1)) {
  if (sp[r] == "Lancetfish") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 122 | SPECIES_CODE == 121) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 500) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 122 | SPECIES_CODE == 121) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 500) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "BigeyeTuna") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 211) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 211) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "BlueShark") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 418) |> 
      filter(MEAS1_TYPE_ID == 4415) |> # in-protocol approximate length in ft
      filter(!is.na(MEAS1) & MEAS1 < 17) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # ft to cm (note that this will make a blocky weight distribution)
    # 1 ft = 30.48 cm
    ObsDeep_hold$MEAS1 <- ObsDeep_hold$MEAS1 * 30.48
    # Convert estimated TL to estimated PCL
    # PCL = (TL × 0.748) + 1.063
    ObsDeep_hold$MEAS1 <- (ObsDeep_hold$MEAS1 * 0.748) + 1.063
    # Average across males and females, in g rather than kg
    Deep_m <- (3.291e-6 * 1000) * ObsDeep_hold$MEAS1^3.225
    Deep_f <- (5.388e-6 * 1000) * ObsDeep_hold$MEAS1^3.102
    Deep_w <- (Deep_m + Deep_f)/2
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 418) |> 
      filter(MEAS1_TYPE_ID == 4415) |> # in-protocol approximate length in ft
      filter(!is.na(MEAS1) & MEAS1 < 17) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # ft to cm (note that this will make a blocky weight distribution)
    # 1 ft = 30.48 cm
    ObsShal_hold$MEAS1 <- ObsShal_hold$MEAS1 * 30.48
    # Convert estimated TL to estimated PCL
    # PCL = (TL × 0.748) + 1.063
    ObsShal_hold$MEAS1 <- (ObsShal_hold$MEAS1 * 0.748) + 1.063
    # Average across males and females, in g rather than kg
    Shal_m <- (3.291e-6 * 1000) * ObsShal_hold$MEAS1^3.225
    Shal_f <- (5.388e-6 * 1000) * ObsShal_hold$MEAS1^3.102
    Shal_w <- (Shal_m + Shal_f)/2
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "MahiMahi") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 218 | SPECIES_CODE == 219) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 500) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # Average across males and females, in g rather than kg
    Deep_m <- (8.09e-6 * 1000) * ObsDeep_hold$MEAS1^3.0157
    Deep_f <- (1.07e-5 * 1000) * ObsDeep_hold$MEAS1^2.9337
    Deep_w <- (Deep_m + Deep_f)/2
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 218 | SPECIES_CODE == 219) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 500) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # Average across males and females, in g rather than kg
    Shal_m <- (8.09e-6 * 1000) * ObsShal_hold$MEAS1^3.0157
    Shal_f <- (1.07e-5 * 1000) * ObsShal_hold$MEAS1^2.9337
    Shal_w <- (Shal_m + Shal_f)/2
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "Swordfish") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 301) |> 
      filter(MEAS1_TYPE_ID == 1350) |> # in-protocol EFL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 301) |> 
      filter(MEAS1_TYPE_ID == 1350) |> # in-protocol EFL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "YellowfinTuna") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 216) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 216) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "SkipjackTuna") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 212) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 212) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "AlbacoreTuna") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 215) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 215) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "StripedMarlin") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 302) |> 
      filter(MEAS1_TYPE_ID == 1350) |> # in-protocol EFL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 500) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 302) |> 
      filter(MEAS1_TYPE_ID == 1350) |> # in-protocol EFL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 500) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "Wahoo") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 221) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 221) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "Opah") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 144) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # Average across male, female, and unknown using weight in g not kg
    Deep_m <- exp(2.5692 * log(ObsDeep_hold$MEAS1) - 8.2368) * 1000
    Deep_f <- exp(2.5815 * log(ObsDeep_hold$MEAS1) - 8.3378) * 1000
    Deep_u <- exp(2.7332 * log(ObsDeep_hold$MEAS1) - 9.084) * 1000
    Deep_w <- (Deep_m + Deep_f + Deep_u) / 3
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 144) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # Average across male, female, and unknown using weight in g not kg
    Shal_m <- exp(2.5692 * log(ObsShal_hold$MEAS1) - 8.2368) * 1000
    Shal_f <- exp(2.5815 * log(ObsShal_hold$MEAS1) - 8.3378) * 1000
    Shal_u <- exp(2.7332 * log(ObsShal_hold$MEAS1) - 9.084) * 1000
    Shal_w <- (Shal_m + Shal_f + Shal_u) / 3
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "BlueMarlin") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 305) |> 
      filter(MEAS1_TYPE_ID == 1350) |> # in-protocol EFL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 350) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # Average across male, female, and unknown using weight in g not kg
    Deep_m <- (1.37e-5 * 1000) * ObsDeep_hold$MEAS1^2.975
    Deep_f <- (1.84e-5 * 1000) * ObsDeep_hold$MEAS1^2.956
    Deep_w <- (Deep_m + Deep_f) / 2
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 305) |> 
      filter(MEAS1_TYPE_ID == 1350) |> # in-protocol EFL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 350) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # Average across male, female, and unknown using weight in g not kg
    Shal_m <- (1.37e-5 * 1000) * ObsShal_hold$MEAS1^2.975
    Shal_f <- (1.84e-5 * 1000) * ObsShal_hold$MEAS1^2.956
    Shal_w <- (Shal_m + Shal_f) / 2
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "ShortfinMakoShark") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 432) |> 
      filter(MEAS1_TYPE_ID == 4415) |> # in-protocol approximate length in ft
      filter(!is.na(MEAS1) & MEAS1 < 14) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # ft to cm (note that this will make a blocky weight distribution)
    # 1 ft = 30.48 cm
    ObsDeep_hold$MEAS1 <- ObsDeep_hold$MEAS1 * 30.48
    # Convert estimated TL to estimated PCL
    # PCL = (TL × 0.816) + 0.784
    ObsDeep_hold$MEAS1 <- (ObsDeep_hold$MEAS1 * 0.816) + 0.784
    # Average across males and females, in g rather than kg
    Deep_m <- (4.62e-5 * 1000) * ObsDeep_hold$MEAS1^2.77
    Deep_f <- (3.40e-5 * 1000) * ObsDeep_hold$MEAS1^2.84
    Deep_w <- (Deep_m + Deep_f)/2
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 432) |> 
      filter(MEAS1_TYPE_ID == 4415) |> # in-protocol approximate length in ft
      filter(!is.na(MEAS1) & MEAS1 < 14) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # ft to cm (note that this will make a blocky weight distribution)
    # 1 ft = 30.48 cm
    ObsShal_hold$MEAS1 <- ObsShal_hold$MEAS1 * 30.48
    # Convert estimated TL to estimated PCL
    # PCL = (TL × 0.816) + 0.784
    ObsShal_hold$MEAS1 <- (ObsShal_hold$MEAS1 * 0.816) + 0.784
    # Average across males and females, in g rather than kg
    Shal_m <- (4.62e-5 * 1000) * ObsShal_hold$MEAS1^2.77
    Shal_f <- (3.40e-5 * 1000) * ObsShal_hold$MEAS1^2.84
    Shal_w <- (Shal_m + Shal_f)/2
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "Pomfret") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 189 | SPECIES_CODE == 188 | SPECIES_CODE == 187 | 
               SPECIES_CODE == 185 | SPECIES_CODE == 183 | SPECIES_CODE == 184 | 
               SPECIES_CODE == 186 | SPECIES_CODE == 180) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 189 | SPECIES_CODE == 188 | SPECIES_CODE == 187 | 
               SPECIES_CODE == 185 | SPECIES_CODE == 183 | SPECIES_CODE == 184 | 
               SPECIES_CODE == 186 | SPECIES_CODE == 180) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "ShortbillSpearfish") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 303) |> 
      filter(MEAS1_TYPE_ID == 1350) |> # in-protocol EFL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 303) |> 
      filter(MEAS1_TYPE_ID == 1350) |> # in-protocol EFL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "OceanicWhitetipShark") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 419) |> 
      filter(MEAS1_TYPE_ID == 4415) |> # in-protocol approximate length in ft
      filter(!is.na(MEAS1)) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # ft to cm (note that this will make a blocky weight distribution)
    # 1 ft = 30.48 cm
    ObsDeep_hold$MEAS1 <- ObsDeep_hold$MEAS1 * 30.48
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 419) |> 
      filter(MEAS1_TYPE_ID == 4415) |> # in-protocol approximate length in ft
      filter(!is.na(MEAS1)) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    # ft to cm (note that this will make a blocky weight distribution)
    # 1 ft = 30.48 cm
    ObsShal_hold$MEAS1 <- ObsShal_hold$MEAS1 * 30.48
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "SnakeMackerel") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 193) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 193) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1)) |> # omit missing values 
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
  
  if (sp[r] == "Escolar") {
    ObsDeep_hold <- ObsDeep |>
      filter(SPECIES_CODE == 191 | SPECIES_CODE == 192 | SPECIES_CODE == 197 | 
               SPECIES_CODE == 196) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 500) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Deep_w <- pelagic_species_params$a[r] * ObsDeep_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    d <- hist(Deep_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    DeepN[r,] <- d$counts
    DeepN_n[r,1] <- length(Deep_w)
    
    ObsShal_hold <- ObsShal |>
      filter(SPECIES_CODE == 191 | SPECIES_CODE == 192 | SPECIES_CODE == 197 | 
               SPECIES_CODE == 196) |> 
      filter(MEAS1_TYPE_ID == 1348) |> # in-protocol FL to the nearest cm
      filter(!is.na(MEAS1) & MEAS1 < 500) |> # omit missing values and outliers
      select(MEAS1) # Just keep the lengths
    # Convert L to W
    Shal_w <- pelagic_species_params$a[r] * ObsShal_hold$MEAS1^pelagic_species_params$b[r]
    # Bin
    s <- hist(Shal_w, breaks = c(w, (w[100] + dw[100])), plot = FALSE)
    # Fill matrices
    ShalN[r,] <- s$counts
    ShalN_n[r,1] <- length(Shal_w)
  }
}

# Clean up
rm(d, s, r, ObsDeep_hold, ObsShal_hold, 
   Deep_f, Deep_m, Deep_w, 
   Shal_f, Shal_m, Shal_w)
```

Identify species-specific fishing parameters: sigmoidal weight and sigmoidal
sigma. For more on fishing in mizer see <https://sizespectrum.org/mizer/reference/gear_params.html>
and <https://sizespectrum.org/mizer/reference/sigmoid_weight.html>.
```{r}
# Set sigmoidal_weight as the smallest size with at least 25% of max catch
# Set sigmoidal_sigmal as the width of sizes caught
# Doing this as simply as possible to start, to see how it works.
pelagic_deep_params <- data.frame(
  species  = sp,
  gear = rep("DeepSet", length(sp)),
  catchability = pelagic_species_params$catchability,
  sel_func = rep("sigmoid_weight", length(sp)),
  sigmoidal_weight = rep(NA, length(sp)), # We're going to loop through and fill this
  sigmoidal_sigma =  rep(NA, length(sp)) # We're going to loop through and fill this
)

pelagic_shallow_params <- data.frame(
  species  = sp,
  gear = rep("ShallowSet", length(sp)),
  catchability = pelagic_species_params$catchability,
  sel_func = rep("sigmoid_weight", length(sp)),
  sigmoidal_weight = rep(NA, length(sp)), # We're going to loop through and fill this
  sigmoidal_sigma =  rep(NA, length(sp)) # We're going to loop through and fill this
)

for (s in seq(1, length(sp), 1)) {
  # Find the index for the maximum weight
  d_max <- which(DeepN[s,] >= (max(DeepN[s,]) * 0.25))
  s_max <- which(ShalN[s,] >= (max(ShalN[s,]) * 0.25))
  
  # Put the corresponding size in the params data frame
  pelagic_deep_params$sigmoidal_weight[s] <- w[min(d_max)]
  pelagic_shallow_params$sigmoidal_weight[s] <- w[min(s_max)]
  
  # Find sizes that have at least 1% of the catch of max catch size
  d_nz <- which(DeepN[s,] >= (max(DeepN[s,]) * 0.01))
  s_nz <- which(ShalN[s,] >= (max(ShalN[s,]) * 0.01))
  
  # Put the inclusive range in the params data frame
  pelagic_deep_params$sigmoidal_sigma[s] <- (max(d_nz) - min(d_nz) + 1)
  pelagic_shallow_params$sigmoidal_sigma[s] <- (max(s_nz) - min(s_nz) + 1)
}

# Clean up
rm(s, d_max, s_max, d_nz, s_nz)

# Combine, for saving
pelagic_gear_params <- rbind(pelagic_deep_params, pelagic_shallow_params)
```


Plot things
```{r}
# pdf(here("ModelBuild", "FisheryData", "DeepSet_SizeStructure.pdf"))
par(mfrow = c(3,6))
for (s in seq(1, 18, 1)) {
  plot(log10(w), DeepN[s,], type = "l", xlim = c(-3, 6), main = sp[s],
       xlab = "log10(body weight in grams)", ylab = "Number Caught")
  points(log10(pelagic_deep_params$sigmoidal_weight[s]), max(DeepN[s,]*0.25), 
         col = "deepskyblue", xlim = c(-3, 6))
  lines(x = c(min(log10(w[which(DeepN[s,] >= (max(DeepN[s,]) * 0.01))])), max(log10(w[which(DeepN[s,] >= (max(DeepN[s,]) * 0.01))]))),
        y = c(0.01*max(DeepN[s,]), 0.01*max(DeepN[s,])),
        col = "deepskyblue", xlim = c(-3,6), yaxt = "n")
  text(-2, 0.8*max(DeepN[s,]), paste0("n = ", DeepN_n[s,1]))
}
# dev.off()

# pdf(here("ModelBuild", "FisheryData", "ShallowSet_SizeStructure.pdf"))
par(mfrow = c(3,6))
for (s in seq(1, 18, 1)) {
  plot(log10(w), ShalN[s,], type = "l", xlim = c(-3, 6), main = sp[s],
       xlab = "log10(body weight in grams)", ylab = "Number Caught")
  points(log10(pelagic_shallow_params$sigmoidal_weight[s]), max(ShalN[s,]*0.25), 
         col = "deepskyblue", xlim = c(-3, 6))
  lines(x = c(min(log10(w[which(ShalN[s,] >= (max(ShalN[s,]) * 0.01))])), max(log10(w[which(ShalN[s,] >= (max(ShalN[s,]) * 0.01))]))),
        y = c(0.01*max(ShalN[s,]), 0.01*max(ShalN[s,])),
        col = "deepskyblue", xlim = c(-3,6), yaxt = "n")
  text(-2, 0.8*max(ShalN[s,]), paste0("n = ", ShalN_n[s,1]))
}
# dev.off()
```
Note: The shark distributions are blocky because their lengths are measured in 
feet instead of in cm.  

We need to add row names to the gear parameters, by pasting together the species
name and the gear name, separating them by a comma.
```{r}
gear_row_names <- paste(pelagic_gear_params$species, pelagic_gear_params$gear, sep = ", ")
row.names(pelagic_gear_params) <- gear_row_names
```

Save things
```{r}
# write_csv(as.data.frame(DeepN), here("ModelBuild", "FisheryData", "DeepSet_CatchAtSize.csv"))
# write_csv(as.data.frame(ShalN), here("ModelBuild", "FisheryData", "ShallowSet_CatchAtSize.csv"))
# 
# write_csv(as.data.frame(DeepN_n), here("ModelBuild", "FisheryData", "DeepSet_CatchCounts.csv"))
# write_csv(as.data.frame(ShalN_n), here("ModelBuild", "FisheryData", "ShallowSet_CatchCounts.csv"))
# 
# write.csv(pelagic_gear_params, here("Pelagic_gear_params_25_1.csv"), row.names = TRUE)
```

Figure for model overview (to be refined in Illustrator)
```{r}
s <- 2
# pdf(here("ModelBuild", "FisheryData", "BigeyeExample.pdf"), width = 6, height = 4)
par(mfrow = c(1,1))
plot(log10(w), DeepN[s,], type = "l", xlim = c(-3, 6), main = sp[s],
     xlab = "log10(body weight in grams)", ylab = "Number Caught", yaxt = "n")
points(log10(pelagic_deep_params$sigmoidal_weight[s]), max(DeepN[s,]*0.25), 
       col = "#008da8", xlim = c(-3, 6), yaxt = "n")
lines(x = c(min(log10(w[which(DeepN[s,] >= (max(DeepN[s,]) * 0.01))])), max(log10(w[which(DeepN[s,] >= (max(DeepN[s,]) * 0.01))]))),
      y = c(0.01*max(DeepN[s,]), 0.01*max(DeepN[s,])),
      col = "#008da8", xlim = c(-3,6), yaxt = "n")
text(-2, 0.8*max(DeepN[s,]), paste0("n = ", DeepN_n[s,1]), yaxt = "n")
axis((2), las = 1)
# dev.off()
```





