# Species parameters {#sec-SpeciesParams}

Gathering needed species parameters is probably the biggest job in building a 
mizer model, particularly if you're working with poorly understood species in a
data-poor region.  Working with a team makes the job easier[^1]. It also helps
that mizer will estimate many parameters for you based on sound science.  See
their [site](https://sizespectrum.org/mizer/) for more.

[^1]: To borrow advice from a fellow [Openscapes](https://nmfs-openscapes.github.io/)
mentor, "never work alone."

To start, we gathered the parameters listed in @tbl-params by consulting the 
corresponding references listed in @tbl-refs.  While these tables look nice and
tidy, there was ample background work involved.  Our team had a shared Google 
doc where we noted parameters and left helpful feedback for one another.  The
final parameters were added to a data frame using a [script](https://github.com/noaa-pifsc/Pelagic-mizer-model/blob/main/ModelBuild/Build_species_params.Rmd),
although you could absolutely do this step in the spreadsheet editor of your choice
(and it would probably be easier).

In @tbl-params, the NA values for weight-related parameters (e.g., *w_mat*, 
*w_max*) indicate weights that are converted from lengths using the *a* and *b*
parameters.  NA values for *a* and *b* parameters indicate sexually dimorphic
species.  In these cases, weights are calculated for each sex and then averaged.
NA values for length-related parameters (e.g., *l_mat*, *l_max*) indicate 
species for which the cooresponding weights were available without conversion. 
These NA values all carry through to @tbl-refs.

In @tbl-refs, default indicates paramters that were estimated following the 
[prior](https://www.frontiersin.org/journals/marine-science/articles/10.3389/fmars.2019.00383/full)
methodology: 

* *w_min*: all teleosts enter at 1 mg 
* *R_max*: scaled from maximum body size as 10^11^ $\times$ *w~max~*^-1.5^ (@Blanchard2014) 
* *w_min*: species' minimum depth is 0 m in the absence of evidence to the contrary

Each species' minimum and maximum depths (*depth_min* and *depth_max*, 
respectively) were used by a [script](https://github.com/noaa-pifsc/Pelagic-mizer-model/blob/main/ModelBuild/Build_interaction_matrix.Rmd)
to build the interaction matrix (@tbl-inter) based on vertical overlap (see the 
[original model](https://www.frontiersin.org/journals/marine-science/articles/10.3389/fmars.2019.00383/full)
for more details).  These depth ranges were typical depth ranges, not record
observations, because we want species' routine overlap.  

Note that both pomfret and escolar are species complexes due to changes in 
observer reporting over time.  We leaned towards drawing upon references for the
dominant species in each group wherever possible.

```{r}
#| echo: false
#| message: false
#| label: tbl-params
#| tbl-cap: Species parameters provided to mizer for this model

# Load the libraries we'll need
library(tidyverse, quietly = TRUE)
library(knitr)
library(here)

# Load the table data
params <- read_csv(here("OverviewContent", "Pelagic_params.csv"))

# Make the table
kable(params)
```

```{r}
#| echo: false
#| message: false
#| label: tbl-refs
#| tbl-cap: References for species parameters provided to mizer for this model

# Load the table data
refs <- read_csv(here("OverviewContent", "Pelagic_params_refs.csv"))

# Make the table

kable(refs)
```

```{r}
#| echo: false
#| message: false
#| label: tbl-inter
#| tbl-cap: Interaction matrix with rows being predators and columns being prey

# Load the table data
inter <- read_csv(here("OverviewContent", "Pelagic_interaction.csv"))

# Make the table
kable(inter)
```