# Species parameters {#sec-SpeciesParams}

Gathering needed species parameters is probably the biggest job in building a 
mizer model, particularly if you're working with poorly understood species in a
data-poor region.  Working with a team makes the job easier[^1]. It also helps
that mizer will estimate many parameters for you based on sound science.  See
their [site](https://sizespectrum.org/mizer/) for more.

[^1]: To borrow advice from a fellow [Openscapes](https://nmfs-openscapes.github.io/)
mentor, "never work alone."

To start, we gathered the parameters listed in @tbl-params by consulting the 
corresponding references listed in @tbl-refs.  While these tables look nice and
tidy, there was ample background work involved.  Our team had a shared Google 
doc where we noted parameters and left helpful feedback for one another.  The
final parameters were added to a data frame using a [script](https://github.com/noaa-pifsc/Pelagic-mizer-model/blob/main/ModelBuild/Build_species_params.Rmd),
although you could absolutely do this step in the spreadsheet editor of your choice
(and it would probably be easier).

In @tbl-params, the NA values for weight-related parameters (e.g., *w_mat*, 
*w_max*) indicate weights that are converted from lengths using the *a* and *b*
parameters.  NA values for *a* and *b* parameters indicate sexually dimorphic
species.  In these cases, weights are calculated for each sex and then averaged.
NA values for length-related parameters (e.g., *l_mat*, *l_max*) indicate 
species for which the corresponding weights were available without conversion. 
These NA values all carry through to @tbl-refs.

In @tbl-refs, default indicates parameters that were estimated following the 
[prior](https://www.frontiersin.org/journals/marine-science/articles/10.3389/fmars.2019.00383/full)
methodology: 

* *w_min*: all teleosts enter at 1 mg 
* *R_max*: scaled from maximum body size as 10^11^ $\times$ *w~max~*^-1.5^ (@Blanchard2014) 
* *w_min*: species' minimum depth is 0 m in the absence of evidence to the contrary

Expert Opinion notes rare instances when insufficient data were available in the
literature and the authors used their best judgement based on information 
available for similar species and/or life history parameters.  Each species' 
minimum and maximum depths (*depth_min* and *depth_max*, respectively) were used 
by a [script](https://github.com/noaa-pifsc/Pelagic-mizer-model/blob/main/ModelBuild/Build_interaction_matrix.Rmd)
to build the interaction matrix (@tbl-inter) based on vertical overlap (see the 
[original model](https://www.frontiersin.org/journals/marine-science/articles/10.3389/fmars.2019.00383/full)
for more details).  These depth ranges were typical depth ranges, not record
observations, because we want species' typical overlap.  

We include the following species in our model:  

* Lancetfish (*Alepisaurus ferox*)
* Bigeye Tuna (*Thunnus obesus*)
* Blue Shark (*Prionace glauca*)
* Mahi Mahi (*Coryphaena hippurus*)
* Swordfish (*Xiphiaus gladius*)
* Yellowfin Tuna (*Thunnus albacares*) 
* Skipjack Tuna (*Katsuwonus pelamis*)
* Albacore Tuna (*Thunnus alalunga*)
* Striped Marlin (*Kajikia audax*)
* Wahoo (*Acanthocybium solandri*)
* Opah (*Lampris guttatus*)
* Blue Marlin (*Makaira nigricans*)
* Shortfin Mako Shark (*Isurus oxyrinchus*)
* Pomfret (species complex, see below)
* Shortbill Spearfish (*Tetrapturus angustirostris*)
* Oceanic Whitetip Shark (*Carcharhinus longimanus*)
* Snake Mackerel (*Gempylus serpens*)
* Escolar (species complex, see below)

Note that both pomfret and escolar are species complexes due to changes in 
observer reporting over time.  We leaned towards drawing upon references for the
dominant species in each group wherever possible.

We used the following species parameters:

* *species*: names for each species in the model, keep these in the same order
across all your code and data
* *w_max*: maximum mass in grams for each species, generally observed maximum 
rather than asymptotic
* *w_mat*: mass in grams at maturity, we use $W_{50}$
* *age_mat*: age in years at maturity
* *w_min*: minimum mass in grams
* *R_max*: maximum reproduction rate
* *depth_min*: typical minimum depth in meters
* *depth_max*: typical maximum depth in meters
* *beta*: preferred predator-prey mass ratio
* *sigma*: width of the lognormal feeding kernel	
* *a*: length-weight conversion factor, used as $W = aL^b$
* *b*:  length-weight conversion factor, used as $W = aL^b$
* *l_min*: minimum length in cm
* *l_mat*: length at maturity, we use $L_{50}$
* *l_max*: maximum length in cm, generally observed maximum rather than 
asymptotic
* *catchability*: see @sec-FishingParams  

Note that this list of parameters doesn't exactly match those used during in the 
[prior](https://www.frontiersin.org/journals/marine-science/articles/10.3389/fmars.2019.00383/full)
model due to updates to the mizer model itself. See the [mizer site](https://sizespectrum.org/mizer/) for further details and additional parameters.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-params
#| tbl-cap: Species parameters provided to mizer for this model

# Load the libraries we'll need
library(tidyverse, quietly = TRUE)
library(knitr)
library(here)

# Load the table data
params <- read_csv(here("OverviewContent", "Pelagic_params.csv"))

# Make the table
kable(params)
```

```{r}
#| echo: false
#| message: false
#| label: tbl-refs
#| tbl-cap: References for species parameters provided to mizer for this model

# Load the table data
refs <- read_csv(here("OverviewContent", "Pelagic_params_refs.csv"))

# Make the table

kable(refs)
```

```{r}
#| echo: false
#| message: false
#| label: tbl-inter
#| tbl-cap: Interaction matrix with rows being predators and columns being prey

# Load the table data
inter <- read_csv(here("OverviewContent", "Pelagic_interaction.csv"))

# Make the table
kable(inter)
```
