---
title: "Build_species_params"
output: html_document
---

# Purpose
The purpose of this script is to build the species parameters data frame and to 
keep track of references at the same time.

```{r, message = FALSE} 
# In the above line, `message = FALSE` suppresses some ignorable R messages
# You can delete `, message = FALSE` if you want to see the messages

# Set up the workspace
library(tidyverse, quietly = TRUE) # handy for working with data frames
library(here) # file path management that works on any operating system
```

# Initial data frames
This code builds the initial empty data frames.  Start here if you're starting 
from scratch.  If you want to add new information, skip down to the section on 
updating the data frames.
```{r}
# Build empty data frames 
species_params <- data.frame(matrix(nrow = 8, ncol = 2,
                                    dimnames = list(NULL, c("species",
                                                            "w_max"))))

species_params_refs <- data.frame(matrix(nrow = 8, ncol = 2,
                                         dimnames = list(NULL, c("species",
                                                                 "w_max"))))

# Add the first species to each, picking ones we're certain to use
species_params$species <- c("Lancetfish",
                            "BigeyeTuna", 
                            "BlueShark", 
                            "MahiMahi", 
                            "Swordfish",
                            "YellowfinTuna",
                            "SkipjackTuna",
                            "AlbacoreTuna")
species_params_refs$species <- c("Lancetfish", 
                                 "BigeyeTuna", 
                                 "BlueShark", 
                                 "MahiMahi", 
                                 "Swordfish",
                                 "YellowfinTuna", 
                                 "SkipjackTuna", 
                                 "AlbacoreTuna")
```

# Update the data frames with parameters
This code lets you add information to the data frames.  Start here if you're 
loading the partially built parameters and adding to them.

First, create functions to make it easier to add information:
```{r}
add_new_species <- function(df_to_update, species_name) {
  # Add an empty row with the correct number of columns
  new_row <- rep(NA, dim(df_to_update)[2])
  df_to_update <- rbind(df_to_update, new_row)
  
  # Add new species name
  df_to_update$species[dim(df_to_update)[1]] <- species_name
  
  # Return updated parameters
  return(df_to_update)
}

add_param_info <- function(df_to_update, species_name, parameter_name, new_info) {
  # Find the row for the species we want
  rowID <- which(df_to_update$species == species_name)
  
  # Find the column we want to update
  colID <- which(dimnames(df_to_update)[[2]] == parameter_name)
  
  # Update the parameter
  df_to_update[rowID, colID] = new_info
  
  # Return updated parameters
  return(df_to_update)
}
```

Load the existing parameters:
```{r}
# To be written if used
```

To add a new parameter, use the `mutate` function:
```{r}
# Add an empty column with the parameter name.  Here, that's w_min and w_mat
species_params <- species_params |>
  mutate(w_min = NA) |>
  mutate(w_mat = NA) |>
  mutate(depth_min = NA) |>
  mutate(depth_max = NA) |>
  mutate(beta = NA) |>
  mutate(sigma = NA) |>
  mutate(age_mat = NA)

species_params_refs <- species_params_refs |>
  mutate(w_min = NA) |>
  mutate(w_mat = NA)|>
  mutate(depth_min = NA) |>
  mutate(depth_max = NA) |>
  mutate(beta = NA) |>
  mutate(sigma = NA) |>
  mutate(age_mat = NA)
```

Now, use the functions:
```{r}
# species_params <- add_new_species(species_params, "YellowfinTuna")
# species_params_refs <- add_new_species(species_params_refs, "YellowfinTuna")
# 
# w_min
species_params <- add_param_info(species_params, "Lancetfish", "w_min", 0.001)
species_params_refs <- add_param_info(species_params_refs, "Lancetfish", "w_min", 
                                 "default")

species_params <- add_param_info(species_params, "BigeyeTuna", "w_min", 0.001)
species_params_refs <- add_param_info(species_params_refs, "BigeyeTuna", "w_min", 
                                 "default")

species_params <- add_param_info(species_params, "MahiMahi", "w_min", 0.001)
species_params_refs <- add_param_info(species_params_refs, "MahiMahi", "w_min", 
                                 "default")

species_params <- add_param_info(species_params, "BlueShark", "w_min", 353)
species_params_refs <- add_param_info(species_params_refs, "BlueShark", "w_min", 
                                 "@ISC2022")

species_params <- add_param_info(species_params, "Swordfish", "w_min", 0.001)
species_params_refs <- add_param_info(species_params_refs, "Swordfish", "w_min", 
                                 "default")

species_params <- add_param_info(species_params, "YellowfinTuna", "w_min", 0.001)
species_params_refs <- add_param_info(species_params_refs, "YellowfinTuna", "w_min", 
                                 "default")

species_params <- add_param_info(species_params, "SkipjackTuna", "w_min", 0.001)
species_params_refs <- add_param_info(species_params_refs, "SkipjackTuna", "w_min", 
                                 "default")

species_params <- add_param_info(species_params, "AlbacoreTuna", "w_min", 0.001)
species_params_refs <- add_param_info(species_params_refs, "AlbacoreTuna", "w_min", 
                                 "default")

# w_mat & age_mat
species_params <- add_param_info(species_params, "Lancetfish", "w_mat", 109)
species_params_refs <- add_param_info(species_params_refs, "Lancetfish", "w_mat", 
                                 "@Gibbs1960, @Uchiyama2003")
species_params <- add_param_info(species_params, "Lancetfish", "age_mat", 3)
species_params_refs <- add_param_info(species_params_refs, "Lancetfish", "age_mat", 
                                 "@Thorson2023, ExpertOpinion")


species_params <- add_param_info(species_params, "BigeyeTuna", "w_mat", 25373)
species_params_refs <- add_param_info(species_params_refs, "BigeyeTuna", "w_mat", 
                                 "@Farley2018, @Uchiyama2003")
species_params <- add_param_info(species_params, "BigeyeTuna", "age_mat", 2.85)
species_params_refs <- add_param_info(species_params_refs, "BigeyeTuna", "age_mat", 
                                 "@Farley2018")

species_params <- add_param_info(species_params, "MahiMahi", "w_mat", 1024)
species_params_refs <- add_param_info(species_params_refs, "MahiMahi", "w_mat", 
                                 "@AlejoPlata2011, @Uchiyama2003")
species_params <- add_param_info(species_params, "MahiMahi", "age_mat", 0.4)
species_params_refs <- add_param_info(species_params_refs, "MahiMahi", "age_mat", 
                                 "@Perrichon2019")

species_params <- add_param_info(species_params, "BlueShark", "w_mat", 38867)
species_params_refs <- add_param_info(species_params_refs, "BlueShark", "w_mat", 
                                 "@ISC2022")
species_params <- add_param_info(species_params, "BlueShark", "age_mat", 5.75)
species_params_refs <- add_param_info(species_params_refs, "BlueShark", "age_mat", 
                                 "@ISC2022")

species_params <- add_param_info(species_params, "Swordfish", "w_mat", 37019)
species_params_refs <- add_param_info(species_params_refs, "Swordfish", "w_mat", 
                                 "@DeMartini2000, @DeMartini2007")
species_params <- add_param_info(species_params, "Swordfish", "age_mat", 2)
species_params_refs <- add_param_info(species_params_refs, "Swordfish", "age_mat", 
                                 "@DeMartini2000, @DeMartini2007")

species_params <- add_param_info(species_params, "YellowfinTuna", "w_mat", 25085)
species_params_refs <- add_param_info(species_params_refs, "YellowfinTuna", "w_mat", 
                                 "@Uchiyama2003, @Itano2000, @Magnusson2023")
species_params <- add_param_info(species_params, "YellowfinTuna", "age_mat", 2)
species_params_refs <- add_param_info(species_params_refs, "YellowfinTuna", "age_mat", 
                                 "@Magnusson2023")

species_params <- add_param_info(species_params, "SkipjackTuna", "w_mat", 1757)
species_params_refs <- add_param_info(species_params_refs, "SkipjackTuna", "w_mat", 
                                 "@Jordan2022, @Uchiyama2003")
species_params <- add_param_info(species_params, "SkipjackTuna", "age_mat", 0.5)
species_params_refs <- add_param_info(species_params_refs, "SkipjackTuna", "age_mat", 
                                 "@Jordan2022")

species_params <- add_param_info(species_params, "AlbacoreTuna", "w_mat", 14722)
species_params_refs <- add_param_info(species_params_refs, "AlbacoreTuna", "w_mat", 
                                 "@Uchiyama2003, @AlbacoreWG")
species_params <- add_param_info(species_params, "AlbacoreTuna", "age_mat", 5)
species_params_refs <- add_param_info(species_params_refs, "AlbacoreTuna", "age_mat", 
                                 "@AlbacoreWG")

# w_max
species_params <- add_param_info(species_params, "Lancetfish", "w_max", 2873)
species_params_refs <- add_param_info(species_params_refs, "Lancetfish", "w_max", 
                                 "@Portner2017, @Uchiyama2003")

species_params <- add_param_info(species_params, "BigeyeTuna", "w_max", 95200)
species_params_refs <- add_param_info(species_params_refs, "BigeyeTuna", "w_max", 
                                 "@Uchiyama2003")

species_params <- add_param_info(species_params, "MahiMahi", "w_max", 29800)
species_params_refs <- add_param_info(species_params_refs, "MahiMahi", "w_max", 
                                 "@Uchiyama2004")

species_params <- add_param_info(species_params, "BlueShark", "w_max", 119968)
species_params_refs <- add_param_info(species_params_refs, "BlueShark", "w_max", 
                                 "@ISC2017")

species_params <- add_param_info(species_params, "Swordfish", "w_max", 202621)
species_params_refs <- add_param_info(species_params_refs, "Swordfish", "w_max", 
                                 "@DeMartini2007")

species_params <- add_param_info(species_params, "YellowfinTuna", "w_max", 93400)
species_params_refs <- add_param_info(species_params_refs, "YellowfinTuna", "w_max", 
                                 "@Uchiyama2003")

species_params <- add_param_info(species_params, "SkipjackTuna", "w_max", 10400)
species_params_refs <- add_param_info(species_params_refs, "SkipjackTuna", "w_max", 
                                 "@Uchiyama2003")

species_params <- add_param_info(species_params, "AlbacoreTuna", "w_max", 37200)
species_params_refs <- add_param_info(species_params_refs, "AlbacoreTuna", "w_max", 
                                 "@Uchiyama2003")

# depth_min
species_params <- add_param_info(species_params, "Lancetfish", "depth_min", 0)
species_params_refs <- add_param_info(species_params_refs, "Lancetfish", "depth_min", 
                                 "default")

species_params <- add_param_info(species_params, "BigeyeTuna", "depth_min", 0)
species_params_refs <- add_param_info(species_params_refs, "BigeyeTuna", "depth_min", 
                                 "default")

species_params <- add_param_info(species_params, "MahiMahi", "depth_min", 0)
species_params_refs <- add_param_info(species_params_refs, "MahiMahi", "depth_min", 
                                 "default")

species_params <- add_param_info(species_params, "BlueShark", "depth_min", 0)
species_params_refs <- add_param_info(species_params_refs, "BlueShark", "depth_min", 
                                 "default")

species_params <- add_param_info(species_params, "Swordfish", "depth_min", 0)
species_params_refs <- add_param_info(species_params_refs, "Swordfish", "depth_min", 
                                 "default")

species_params <- add_param_info(species_params, "YellowfinTuna", "depth_min", 0)
species_params_refs <- add_param_info(species_params_refs, "YellowfinTuna", "depth_min", 
                                 "default")

species_params <- add_param_info(species_params, "SkipjackTuna", "depth_min", 0)
species_params_refs <- add_param_info(species_params_refs, "SkipjackTuna", "depth_min", 
                                 "default")

species_params <- add_param_info(species_params, "AlbacoreTuna", "depth_min", 0)
species_params_refs <- add_param_info(species_params_refs, "AlbacoreTuna", "depth_min", 
                                 "default")

# depth_max
species_params <- add_param_info(species_params, "Lancetfish", "depth_max", 1200)
species_params_refs <- add_param_info(species_params_refs, "Lancetfish", "depth_max", 
                                 "@Portner2017")

species_params <- add_param_info(species_params, "BigeyeTuna", "depth_max", 500)
species_params_refs <- add_param_info(species_params_refs, "BigeyeTuna", "depth_max", 
                                 "@Howell2010")

species_params <- add_param_info(species_params, "MahiMahi", "depth_max", 85)
species_params_refs <- add_param_info(species_params_refs, "MahiMahi", "depth_max", 
                                 "FishBase")

species_params <- add_param_info(species_params, "BlueShark", "depth_max", 600)
species_params_refs <- add_param_info(species_params_refs, "BlueShark", "depth_max", 
                                 "@Stevens2010")

species_params <- add_param_info(species_params, "Swordfish", "depth_max", 1200)
species_params_refs <- add_param_info(species_params_refs, "Swordfish", "depth_max", 
                                 "@Abecassis2012")

species_params <- add_param_info(species_params, "YellowfinTuna", "depth_max", 250)
species_params_refs <- add_param_info(species_params_refs, "YellowfinTuna", "depth_max", 
                                 "@Lam2020, @Schaefer2011")

species_params <- add_param_info(species_params, "SkipjackTuna", "depth_max", 300)
species_params_refs <- add_param_info(species_params_refs, "SkipjackTuna", "depth_max", 
                                 "@Schaefer2007")

species_params <- add_param_info(species_params, "AlbacoreTuna", "depth_max", 400)
species_params_refs <- add_param_info(species_params_refs, "AlbacoreTuna", "depth_max", 
                                 "@Williams2015, @Duffy2017")

# beta & sigma
species_params <- add_param_info(species_params, "Lancetfish", "beta", 3646)
species_params_refs <- add_param_info(species_params_refs, "Lancetfish", "beta", 
                                 "@Barnes2008")
species_params <- add_param_info(species_params, "Lancetfish", "sigma", 4.0)
species_params_refs <- add_param_info(species_params_refs, "Lancetfish", "sigma", 
                                 "@Barnes2008")

species_params <- add_param_info(species_params, "BigeyeTuna", "beta", 6033)
species_params_refs <- add_param_info(species_params_refs, "BigeyeTuna", "beta", 
                                 "@Barnes2008")
species_params <- add_param_info(species_params, "BigeyeTuna", "sigma", 2.6)
species_params_refs <- add_param_info(species_params_refs, "BigeyeTuna", "sigma", 
                                 "@Barnes2008")

species_params <- add_param_info(species_params, "MahiMahi", "beta", 3646)
species_params_refs <- add_param_info(species_params_refs, "MahiMahi", "beta", 
                                 "@Barnes2008")
species_params <- add_param_info(species_params, "MahiMahi", "sigma", 4.0)
species_params_refs <- add_param_info(species_params_refs, "MahiMahi", "sigma", 
                                 "@Barnes2008")

species_params <- add_param_info(species_params, "BlueShark", "beta", 359)
species_params_refs <- add_param_info(species_params_refs, "BlueShark", "beta", 
                                 "@Barnes2008")
species_params <- add_param_info(species_params, "BlueShark", "sigma", 3.2)
species_params_refs <- add_param_info(species_params_refs, "BlueShark", "sigma", 
                                 "@Barnes2008")

species_params <- add_param_info(species_params, "Swordfish", "beta", 2263)
species_params_refs <- add_param_info(species_params_refs, "Swordfish", "beta", 
                                 "@Barnes2008")
species_params <- add_param_info(species_params, "Swordfish", "sigma", 2.2)
species_params_refs <- add_param_info(species_params_refs, "Swordfish", "sigma", 
                                 "@Barnes2008")

species_params <- add_param_info(species_params, "YellowfinTuna", "beta", 25185)
species_params_refs <- add_param_info(species_params_refs, "YellowfinTuna", "beta", 
                                 "@Barnes2008")
species_params <- add_param_info(species_params, "YellowfinTuna", "sigma", 2.6)
species_params_refs <- add_param_info(species_params_refs, "YellowfinTuna", "sigma", 
                                 "@Barnes2008")

species_params <- add_param_info(species_params, "SkipjackTuna", "beta", 3646)
species_params_refs <- add_param_info(species_params_refs, "SkipjackTuna", "beta", 
                                 "@Barnes2008")
species_params <- add_param_info(species_params, "SkipjackTuna", "sigma", 4.0)
species_params_refs <- add_param_info(species_params_refs, "SkipjackTuna", "sigma", 
                                 "@Barnes2008")

species_params <- add_param_info(species_params, "AlbacoreTuna", "beta", 12453)
species_params_refs <- add_param_info(species_params_refs, "AlbacoreTuna", "beta", 
                                 "@Barnes2008, @Pinnegar2015, @Goni2014")
species_params <- add_param_info(species_params, "AlbacoreTuna", "sigma", 2.7)
species_params_refs <- add_param_info(species_params_refs, "AlbacoreTuna", "sigma", 
                                 "@Barnes2008, @Pinnegar2015, @Goni2014")
```

# Save the updated parameters
If you're happy with your work and want to make it available to the team, save
the new parameter table(s) using the code below.  Remember to push the changes
to the repo.  Otherwise, they'll only live on your computer.
```{r}
# Save the parameters
write_csv(species_params, file = here("Pelagic_params.csv"))
```


